---
title: "Stat385Midterm"
author: "cw"
date: "7/9/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# `Chi-squared Distribution (central or non-central)` was selected for the task

## Create a generic function
```{r}
chisq = function(x, df, ...){
  UseMethod("chisq")
}
mdist = function(x, df, ...){
  UseMethod("mdist")
}
vdist = function(x, df, ...){
  UseMethod("vdist")
}
ddist = function(x, df, ...){
  UseMethod("ddist")
}
pdist = function(x, df, ...){
  UseMethod("pdist")
}
qdist = function(x, df, ...){
  UseMethod("qdist")
}
rdist = function(x, df, ...){
  UseMethod("rdist")
}
```

## Define the generic.default function
I considered to use `if/else if` to discuss the different value of `x`. However, it seems like `R` handles different value of `x` (such as negaive value) very well, so I exclude the `if/else if` for parsimony.
```{r}
chisq.default = function(x, df, ncp = 0, log = FALSE, lower.tail = TRUE, log.p = FALSE) {
  df = df
  mean = df + ncp
  variance = 2*(df + 2*ncp)
  density = dchisq(x, df, ncp = 0, log = FALSE)
  probability = pchisq(x, df, ncp = 0, lower.tail = TRUE, log.p = FALSE)
  quantile = qchisq(x, df, ncp = 0, lower.tail = TRUE, log.p = FALSE)
  random_gen = rchisq(x, df, ncp = 0)
  return(structure(list(df = df,
                        mean = mean, 
                        variance = variance,
                        density = density,
                        probability = probability,
                        quantile = quantile,
                        random_gen = random_gen), 
                   class = "chisq"))
}
```
## Define mdist.chisq()
```{r}
mdist.chisq = function(object, ...){
  mean = object$mean
  return(structure(list(mean = mean), class = "mdist.chisq"))
}
```
## Define vdist.chisq()
```{r}
vdist.chisq = function(object, ...){
  variance = (object$variance)
  return(structure(list(variance = variance), class = "vdist.chisq"))
}
```
## Define ddist.chisq()
```{r}
ddist.chisq = function(object, ...){
  density = object$density
  return(structure(list(density = density), class = "ddist.chisq"))
}
```
## Define pdist.chisq()
```{r}
pdist.chisq = function(object, ...){
  probability = object$probability
  return(structure(list(probability = probability), class = "pdist.chisq"))
}
```
## Define qdist.chisq()
```{r}
qdist.chisq = function(object, ...){
  quantile = object$quantile
  return(structure(list(quantile = quantile), class = "qdist.chisq"))
}
```
## Define rdist.chisq()
```{r}
rdist.chisq = function(object, ...){
  random_gen = object$random_gen
  return(structure(list(random_gen = random_gen), class = "rdist.chisq"))
}
```
## Define default functions
```{r}
mdist.default = function(x, ...) {
  cat("\nIn mdist(x,...), 'x' could only be 'chisq()'. Check the input.\n")
}
vdist.default = function(x, ...) {
  cat("\nIn vdist(x,...), 'x' could only be 'chisq()'. Check the input.\n")
}
ddist.default = function(x, ...) {
  cat("\nIn ddist(x,...), 'x' could only be 'chisq()'. Check the input.\n")
}
pdist.default = function(x, ...) {
  cat("\nIn pdist(x,...), 'x' could only be 'chisq()'. Check the input.\n")
}
qdist.default = function(x, ...) {
  cat("\nIn qdist(x,...), 'x' could only be 'chisq()'. Check the input.\n")
}
rdist.default = function(x, ...) {
  cat("\nIn rdist(x,...), 'x' could only be 'chisq()'. Check the input.\n")
}
```

### Example 0
```{r}                       
mdist(t)                      # check the default message
vdist(t)
ddist(t)
pdist(t)
qdist(t)
rdist(t)
```
### Examples 1
```{r}
x = chisq(1,21) 
mdist(x)
vdist(x)
ddist(x)
pdist(x)
qdist(x)
rdist(x)
```
### Examples 2
```{r, eval= FALSE}
x = chisq(-1,21)    # this line would be ignored
mdist(x)
vdist(x)
ddist(x)
pdist(x)
qdist(x)
rdist(x)
```
### Examples 3
```{r}
x = chisq(0,21)  
mdist(x)
vdist(x)
ddist(x)
pdist(x)
qdist(x)
rdist(x)
```
### Examples 4
```{r}
x = chisq(10,21)  
mdist(x)
vdist(x)
ddist(x)
pdist(x)
qdist(x)         # get NaNs
rdist(x)
```
### Examples 5
```{r}
x = chisq(0.5,21)  
mdist(x)
vdist(x)
ddist(x)
pdist(x)
qdist(x)
rdist(x)         # get an empty vector
```

## Provide a print() function for the results of: mdist(x, ...), vdist(x,...)
```{r}
print.mdist.chisq = function(object, ...){
  cat("\nMean:\n")
  print(object$mean)
}
```
```{r}
print.vdist.chisq = function(object, ...){
  cat("\nVariance:\n")
  print(object$variance)
}
```
### Example 6
```{r}
y = mdist(x)
print(y)
y = vdist(x)
print(y)
```

## Create a summary of randomness vector.
```{r}
summary.mdist.chisq = function(object, ...){
  return(summary = summary(object$mean))
  }
```

```{r}
summary.vdist.chisq = function(object, ...){
  return(summary = summary(object$variance))
  }
```

```{r}
summary.ddist.chisq = function(object, ...){
  return(summary = summary(object$density))
}
```

```{r}
summary.pdist.chisq = function(object, ...){
  return(summary = summary(object$probability))
}
```

```{r}
summary.qdist.chisq = function(object, ...){
  return(summary = summary(object$quantile))
}
```

```{r}
summary.rdist.chisq = function(object, ...){
  return(summary = summary(object$random_gen))
}
```

### Example 7
```{r}
x = chisq(0.5,11)
y = mdist(x)
summary(y)
y = vdist(x)
summary(y)
y = ddist(x)
summary(y)
y = pdist(x)
summary(y)
y = qdist(x)
summary(y)
y = rdist(x)
summary(y)
```